---
title: "`r params$doc_title`"
author: "Brian Erly, MD MPH"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document: default
params:
  doc_title: The Default Title
  data_set: cars
---

## Intro

The purpose of this script is to show how you can make loops in R Markdown, both within the markdown document and in a main script.

```{r cars,echo=FALSE}

library(tidyverse)
library(gluedown)

pseudoWD <- here::here() # Sets the working directory to whereever "COPHS Master Controller.r" is. 


file.Dir <- function(path){
  paste0(pseudoWD,"/",path)
}

data <- file.Dir(
  paste0(
    "data/",
    params$data_set,
    ".csv"
  )
) %>% 
  read_csv()

head(data,6)

summary(data)
```
\newpage

## High Level Report

You can print a high level report of all your data, which is fine for a first order analysis or users who don't need to be restricted.

```{r pressure, echo=FALSE, fig.width=4,fig.heigh=4}

graph_data <- data %>%
  rename(
    x_val = starts_with("xval"),
    y_val = starts_with("yval"),
    category = starts_with("category")
  ) %>%
  select(x_val,y_val,category)

axis_labels <- data %>%
  select(starts_with("xval"),
          starts_with("yval"),
          starts_with("category")) %>%
  colnames() %>%
  sub(".*_", "", .)

xaxislab <- axis_labels[1]
yaxislab <- axis_labels[2]
categorylab <- axis_labels[3]
graph_title <- toupper(params$data_set)
  

ggplot(data = graph_data,
       aes(x=x_val,
           y=y_val
           )
) + 
  geom_point() +
  geom_smooth()+ 
  xlab(xaxislab)+
  ylab(yaxislab) +
  labs(title = graph_title) 
```

And that's neat, but we might want to create individual pages that are specific to an individual category. To do this, we use the package "gluedown".

"Gluedown" is a small set of thoughtful wrappers around the tidyverse package "glue" that will put them in markdown format for you. By using "gluedown" and the chunk setting "results = 'asis', instead of printing consol-ey code output the output will be nicely formatted markdown text. 

```{r gluedown loop, results = 'asis', echo = FALSE, , fig.width=4,fig.heigh=4}
loops <- data %>%
  select(starts_with("category_")) %>%
  unique()

for(i in 1:nrow(loops)){
  
    # Creates a new page for each category
  glue::glue("\n\n\\clearpage\n") %>% print()
  
    # Adds a blank line
  gluedown::md_blank() %>% print()
  
  category_selected <- loops[i,] %>% unlist()
  
  # Print the title for each one-page subreport
  gluedown::md_heading(
    paste0(
      toupper(params$data_set),
      ": category",
      categorylab,
      " = ",
      category_selected
    )
  ) %>%
    print()
  
  # Do a graph for just that category
 g <-  graph_data %>%
    filter(category %in% category_selected) %>%
    ggplot(
       aes(x=x_val,
           y=y_val
           )) + 
  geom_point() +
  geom_smooth()+ 
  xlab(xaxislab)+
  ylab(yaxislab) 
 
 print(g)
  
  
}
